---
title: "Lab4"
author: "Nicholas Stout"
date: "October 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
```


```{r}
summary(av)
```
```{r}
av2 = gather(av, key=Time, Death, c(11,13,15,17,19))
summary(av2)
av3 = gather(av, key=Time_Return, Return, c(12,14,16,18,20))
av2$Return = av3$Return
av2 = select(av2, -c(11:15))
av2$Time = parse_number(av2$Time)
av2 %>% summary()
```

Nicholas Stout: "Of the 173 Avengers on the team, 69 have died at least once."
```{r}
total = nrow(av)
total
claim = filter(av2, Time=="1" & Death=="YES")
num_deaths = nrow(claim)
num_deaths
```
Confirmed: There 69 of the 173 Avengers have died.
```{r}
percent = (num_deaths/total)*100
percent
```
About 40% of the Avengers has died at least once

Isaac Nellans: "There's a 2-in-3 chance that a member of the Avengers returned from their first stint in the afterlife."
```{r}
av2$Return = as.factor(av2$Return)
a = table(av2$Return)
a
pctg = a[names(a)=="YES"]/(a[names(a)=="NO"]+a[names(a)=="YES"])
pctg
```
The pctg variable is the percentage of times that the Avenger who died came back to life. The claim in the article was that this was the case 2/3 of the time. The true value is 64.04%, which is similar to 2/3(or 66.66%).

Dan Tacconi: "I counted 89 total deaths — some unlucky Avengers are basically Meat Loaf with an E-ZPass — and on 57 occasions the individual made a comeback."
```{r}
return1 = filter(av2, Time=="1" & Return=="YES")
return2 = filter(av2, Time=="2" & Return=="YES")
return3 = filter(av2, Time=="3" & Return=="YES")
return4 = filter(av2, Time=="4" & Return=="YES")
return5 = filter(av2, Time=="5" & Return=="YES")

total_return<-nrow(return1)+nrow(return2)+nrow(return3)+nrow(return4)+nrow(return5)
total_return

```
The claim of 57 total comebacks is correct.


jkhkk